---
title: "measurement_html"
author: "Sara Orofino"
date: "4/28/2020"
output: html_document
---

## Theory of Change  
Organization:  American Rivers  
Program Title: American Rivers Fuel Reduction Program  
Region: Sierra Nevada region, specificallly the following four watersheds  
 1. American River Watershed  
 2. Bear River Watershed  
 3. Cosumnes River Watershed  
 4. Yuba River Watershed  

[Insert image of TOC here]  

## Measure Definition

**Measure 1**  

*Measurement goal* :    
*Exact measure to be taken* :    
*Unit of measurement* :    
*Source of data* :    
*Rationale for choice of measure* :    
*Responsibility for data collection* :      
*Frequency of data collection* :  


## Sampling Strategy

**Implementation of Fuels Reduction Program** 

*Target population*: Private land owners/managers in the Sierra Nevada watershed 

*Challenges to representative sampling*: Much of the land in the Sierra Nevada watershed is federally owned not privately owned. Private land owners require permits to implement fuel reduction programs but fuel reduction typically doesn't occur every year and it is unclear if the same land owner would continue to apply for permits in years immediately following implementing a fuel reduction program on their land.  

*Sampling procedure* Random sampling of private land owners in the watershed to determine if they are Cal Fire permit holders, stratified by county since some counties account for a higher proportion of land in the study area. Participants can be mapped to their permit applications by phone number.    

### DeclareDesign()
Declare the population  

```{r measure1-population}
library(DeclareDesign)

# Declare the population 
# baseline proportions are based on the percent each county contributes to the study area
# owner number represents 35% of the number of homeowners in the county, since all homeowners may not have large properties where they are participating in fuel management practices
population <- declare_population(
  county = add_level(N=8, # there are 8 counties in the watershed
         baseline=c(0.36,0.23,0.18,0.5,0.5,0.5,0.5, 0.3)), # % coverage of each county in study area
  owner = add_level(N=c(34000,18000, 10500, 5000, 4000, 2100, 337, 89), 
                      know=draw_binary(baseline))
)
pop <- population()
pop.vector <- c(34000,18000, 10500, 5000, 4000, 2100, 337, 89)

my_estimand <- declare_estimands(mean(know),
                                 label = "Ybar")
```

Reporting and Sampling  
```{r measure1-report-samp}
reporting <- declare_assignment(prob=0.4, #lower probably that any given homeowner would be a burn permit holder
                  assignment_variable = "R")

sampling <- declare_sampling(strata=county,
               strata_n=c(80,80,80,80,80,80,10,10))
```
