---
title: "measurement_html"
author: "Sara Orofino"
date: "4/28/2020"
output: html_document
---

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(kableExtra)
library(DeclareDesign)
```


## Theory of Change  
Organization:  American Rivers  
Program Title: American Rivers Fuel Reduction Program  
Region: Sierra Nevada region, specificallly the following four watersheds  
 1. American River Watershed  
 2. Bear River Watershed  
 3. Cosumnes River Watershed  
 4. Yuba River Watershed  

[Insert image of TOC here]  

## Measure Definition

**Measure 1**  

*Measurement goal* :    
*Exact measure to be taken* :    
*Unit of measurement* :    
*Source of data* :    
*Rationale for choice of measure* :    
*Responsibility for data collection* :      
*Frequency of data collection* :  


## Sampling Strategy

**Measure 1 - Implementation of Fuels Reduction Program** 

*Target population*: Private land owners/managers in the study area

*Challenges to representative sampling*: Much of the land in the Sierra Nevada watershed is federally owned not privately owned, but federal actions involve more factors than simply perception and willingness to pay. Private land owners require permits to implement fuel reduction programs but fuel reduction typically doesn't occur every year and it is unclear if the same land owner would continue to apply for permits in years immediately following implementing a fuel reduction program on their land.  

*Sampling procedure* Random sampling of private land owners in the study area to determine if they are Cal Fire permit holders, stratified by county since some counties account for a higher proportion of land in the study area. 


### DeclareDesign()

Declare the population  
```{r measure1-population}
# baseline = proportion of land area each county contributes to the total study area
# prop = proportion of homeowners in each strata out of the total population (workaround for strata mean function error - see 'measure1-delcare-estimator' code below)
# owner = 35% of the number of homeowners in the county, since all homeowners may not have large properties where they are participating in fuel management practices


population <- declare_population(
  county = add_level(N=8, # there are 8 counties in the watershed
                     baseline=c(0.36,0.23,0.18,0.5,0.5,0.5,0.5, 0.3), # % coverage of each county in study area
                     prop=c(0.459298084, 0.243157809, 0.141842055, 0.067543836, 
                            0.054035069, 0.028368411, 0.004552455, 0.001202280)), #proportion of homeowners in each county
  owner = add_level(N=c(34000,18000, 10500, 5000, 4000, 2100, 337, 89), # 35% of each county's homeowner population
                    know=draw_binary(baseline))
)

pop <- population()
pop.vector <- c(34000,18000, 10500, 5000, 4000, 2100, 337, 89)

my_estimand <- declare_estimands(mean(know),
                                 label = "Ybar")
```

Reporting and Sampling  
```{r measure1-report-samp}
reporting <- declare_assignment(prob=0.4, #lower probably that any given homeowner would be a burn permit holder
                  assignment_variable = "R")

sampling <- declare_sampling(strata=county,
               strata_n=c(80,80,80,80,80,80,10,10)) # sample size 500
```


Declare estimator to calculate the strata weighed mean of the sample to estimate the population    
```{r measure1-declare-estimator}
# function to estimate the population mean using the strata weighted sample mean  
strata_weighted_mean <- function(data){
  data.frame(  
    estimator_label = "strata_w_mean",
    estimand_label = "Ybar",
    n = nrow(data),
    stringsAsFactors = FALSE,
    
    estimate = data %>% filter(R==1) %>%
      group_by(as.factor(county)) %>% # strata by county
      summarise(mean=mean(know), prop=mean(prop)) %>% #work around for prop column error - see below
      # mutate(prop=pop.vector/sum(pop.vector)) %>% 
      mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
      sum()) 
} 
# note: prop column kept throwning me a length error (wanted length 7 not 8), I changed all the other vectors to be length 8 and couldn't figure out why it was requiring a length 7 when the strata and my pop.vector was set to 8. Patrick helped me with a workaround - the prop=mean(prop) gives the proportion of households in the strata based on the prop column we defined in the population setup code.  
```

Measure 1 diagnostics
```{r measure1-diagnosis, cache=TRUE}

answer <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean), 
  estimand = my_estimand) 

design <- population + my_estimand + reporting +
          sampling + answer

diagnosis <- diagnose_design(design, sims = 1000)

diagnosis$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

```


**Measure 4**  

*Measurement goal*: Determine the number of Land owners in high priority sites with willingness to pay for fuel reduction? 
*Exact measure to be taken*: Would you pay for fuel reduction on your property?  yes, depending on cost, no
*Unit of measurement*: yes, depending on cost, no  
*Source of data*: Survey of land owners in high priority areas
*Rationale for choice of measure*: We initially thought of looking into water rights data, that is challenging because it can be challenging to investigate riparian rights in California.  
*Responsibility for data collection*: Third Party Survey Team 
*Frequency of data collection*: Every 1 years  


## Sampling Strategy

**Implementation of Fuels Reduction Program** 

*Target population*: Landowners in high priority areas  

*Challenges to representative sampling*: High priority region of the CABY watershed private lands are generally less productive, steeper, and more isolated than non-federal ownerships. Each property is difficult to find and may have a private driveway and/or PO box. This survey will be sent via mail to American River Contacts and all folks in the high priority areas. Since AR contacts have already connected to a coservation organization their response rate will likelu be higher than the individuals who have not. In addition, AR contacts are more likely to be willing to pay for fuels treatments as they have been working with a conservtaion non-profit so they are already selected for interest in the program. 

*Sampling procedure*: We will survey homeowners in the High Priority region who have interacted with the fuel management educational program and/or live in the CABY high priority regions and ask whether they would be willing to pay for fuels treatment on their property? a. no b. yes. Sampling wil be conducted by a thir  party survey group as residents may be more likely to reposnd yes to American Rivers as they may want to identify with a local consrrvation organizations goals or not admit publicly they would  not be willing to pay. 

### DeclareDesign()
Declare the population  
```{r measure4 -population, echo=TRUE, message=F, eval=TRUE, cache=TRUE}

set.seed(228)
population_4 <- declare_population(
  households_4 = add_level(N=4343, #Homeowners in CABY High  Priority region (35% of CABY region are homeowners, 10% are in high priority areas) 
      AR_contact=draw_binary(N=N, prob = 0.4),
    WTP=correlate(given = AR_contact, rho = 0.5,
                         draw_binary, prob = 0.5)
))
pop_4 <- population_4() #using Declare Design here to create a population of 4343 households, 500 of are AR contacts. #there is a direct correlation between who is already in contact with AR and their willingness to pay for fuels treatment

kable(table(pop_4$AR_contact,pop_4$WTP)) %>% 
  add_header_above(c("AR Contact"=1,"Consent to do Prescribed Burn"=2))

# Generate estimand
my_estimand_4 <- declare_estimands(mean(WTP),
                                 label = "Ybar")

```
Reporting & Sampling 
```{r measure 4 declare report, echo=FALSE, message=F, eval=TRUE }


# Block probabilities represent how likely it is that AR_Contacts or NON-AR_Contacts repond. AR_ Contacts are more likely to repond. 
WTP_report <- declare_assignment(blocks=AR_contact,
                  assignment_variable = "R",
                  block_prob=c(0.3,0.7))

WTP_sample <- declare_sampling(strata=AR_contact,
                             strata_n=c(2895,1448)) # we will oversample nNON AR_contacts to get a better representation of their willingness to pay since they are less likely to report
```


- For residents in contact with AR, the chance of responding is 70%
- For residents not in contact with AR, the chance of responding is 30%
```{r Measure4 strat weight, echo=FALSE, message=F, eval=TRUE}
# What is strata weighted mean? Do we need this? 

strata_weighted_mean_4 <- function(data){
  data.frame(  
  estimator_label = "strata_w_mean",
  estimand_label = "Ybar",
  n = nrow(data),
  stringsAsFactors = FALSE,
 
  estimate = data %>% filter(R==1) %>%
    group_by(AR_contact) %>%
    summarise(mean=mean(WTP)) %>%
    mutate(prop=c(0.3,0.7)) %>%
    mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>%
    sum())
}
```


```{r measure4 diagnosis}

answer_4 <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean),
  estimand = my_estimand_4)

design_4 <- population_4 + my_estimand_4 + WTP_report +
          WTP_sample + answer_4

diagnosis_4 <- diagnose_design(design, sims = 1000)

diagnosis_4$diagnosands_df[,c(4,5,12,14)] %>%
  kable()
```



