---
title: "measurement_html"
author: "Sara Orofino"
date: "4/28/2020"
output: html_document
---

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(kableExtra)
library(DeclareDesign)
```


## Theory of Change  
Organization:  American Rivers  
Program Title: American Rivers Fuel Reduction Program  
Region: Sierra Nevada region, specificallly the following four watersheds  
 1. American River Watershed  
 2. Bear River Watershed  
 3. Cosumnes River Watershed  
 4. Yuba River Watershed  

[Insert image of TOC here]  

## Measure Definition

**Measure 1**  

*Measurement goal* :    
*Exact measure to be taken* :    
*Unit of measurement* :    
*Source of data* :    
*Rationale for choice of measure* :    
*Responsibility for data collection* :      
*Frequency of data collection* :  


## Sampling Strategy

**Measure 1 - Implementation of Fuels Reduction Program** 

*Target population*: Private land owners/managers in the study area

*Challenges to representative sampling*: Much of the land in the Sierra Nevada watershed is federally owned not privately owned, but federal actions involve more factors than simply perception and willingness to pay. Private land owners require permits to implement fuel reduction programs but fuel reduction typically doesn't occur every year and it is unclear if the same land owner would continue to apply for permits in years immediately following implementing a fuel reduction program on their land.  

*Sampling procedure* Random sampling of private land owners in the study area to determine if they are Cal Fire permit holders, stratified by county since some counties account for a higher proportion of land in the study area. 


### DeclareDesign()

Declare the population  
```{r measure1-population}
# baseline = proportion of land area each county contributes to the total study area
# prop = proportion of homeowners in each strata out of the total population (workaround for strata mean function error - see 'measure1-delcare-estimator' code below)
# owner = 35% of the number of homeowners in the county, since all homeowners may not have large properties where they are participating in fuel management practices


population <- declare_population(
  county = add_level(N=8, # there are 8 counties in the watershed
                     baseline=c(0.36,0.23,0.18,0.5,0.5,0.5,0.5, 0.3), # % coverage of each county in study area
                     prop=c(0.459298084, 0.243157809, 0.141842055, 0.067543836, 
                            0.054035069, 0.028368411, 0.004552455, 0.001202280)), #proportion of homeowners in each county
  owner = add_level(N=c(34000,18000, 10500, 5000, 4000, 2100, 337, 89), # 35% of each county's homeowner population
                    know=draw_binary(baseline))
)

pop <- population()
pop.vector <- c(34000,18000, 10500, 5000, 4000, 2100, 337, 89)

my_estimand <- declare_estimands(mean(know),
                                 label = "Ybar")
```

Reporting and Sampling  
```{r measure1-report-samp}
reporting <- declare_assignment(prob=0.4, #lower probably that any given homeowner would be a burn permit holder
                  assignment_variable = "R")

sampling <- declare_sampling(strata=county,
               strata_n=c(80,80,80,80,80,80,10,10)) # sample size 500
```


Declare estimator to calculate the strata weighed mean of the sample to estimate the population    
```{r measure1-declare-estimator}
# function to estimate the population mean using the strata weighted sample mean  
strata_weighted_mean <- function(data){
  data.frame(  
    estimator_label = "strata_w_mean",
    estimand_label = "Ybar",
    n = nrow(data),
    stringsAsFactors = FALSE,
    
    estimate = data %>% filter(R==1) %>%
      group_by(as.factor(county)) %>% # strata by county
      summarise(mean=mean(know), prop=mean(prop)) %>% #work around for prop column error - see below
      # mutate(prop=pop.vector/sum(pop.vector)) %>% 
      mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
      sum()) 
} 
# note: prop column kept throwning me a length error (wanted length 7 not 8), I changed all the other vectors to be length 8 and couldn't figure out why it was requiring a length 7 when the strata and my pop.vector was set to 8. Patrick helped me with a workaround - the prop=mean(prop) gives the proportion of households in the strata based on the prop column we defined in the population setup code.  
```

Measure 1 diagnostics
```{r measure1-diagnosis, cache=TRUE}

answer <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean), 
  estimand = my_estimand) 

design <- population + my_estimand + reporting +
          sampling + answer

diagnosis <- diagnose_design(design, sims = 1000)

diagnosis$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

```


**Measure 4**  

*Measurement goal*: Determine the number of Land owners in high priority sites with willingness to pay for fuel reduction? 
*Exact measure to be taken*: Would you pay for fuel reduction on your property?  yes, depending on cost, no
*Unit of measurement*: yes, depending on cost, no  
*Source of data*: Survey of land owners in high priority areas
*Rationale for choice of measure*: We initially thought of looking into water rights data, that is challenging because it can be challenging to investigate riparian rights in California.  
*Responsibility for data collection*: Third Party Survey Team 
*Frequency of data collection*: Every 1 years  


## Sampling Strategy

**Implementation of Fuels Reduction Program** 

*Target population*: For this measurement our population will be the high priority areas in the Sierra Nevadas(10% of the forest) within the CABY watershed (which is 2,784,640 acres). 1/2 of wildlands in California are privately owned. If we assume this holds true for the portion of the Sierra Nevada region that is high priority, privately owned land will be 139,200 acres. Of those acres private owners how many, after beeing exposed to the programs eduational materials will apply for a CalFire to conduct a prescribed burn on their property. 

Citation: Starrs, Carlin Frances, et al. “The Impact of Land Ownership, Firefighting, and Reserve Status on Fire Probability in California.” Environmental Research Letters, vol. 13, no. 3, IOP Publishing, Feb. 2018, p. 034025. Institute of Physics, doi:10.1088/1748-9326/aaaad1.

*Challenges to representative sampling*: In the high priority region of the CABY watershed private lands are generally less productive, steeper, and more isolated than non-federal ownerships. Each property is difficult to find and may have a private driveway and/or PO box. This survey will be distributed through American River Contacts. Therefor the sampled population may be more inclined to apply for CalFire permits as they have already connected with a forest/water conservation organization. There also may be a lower response rate from homeowners that live in the high priority regions due to the increased isolation and potential challnegs to submitting a survey. 

*Sampling procedure*: We will survey homeowners in the High Priority region who have interacted with the fuel management educational program and ask whether they would consent to a prescribed burn on their property.  

### DeclareDesign()
Declare the population  
```{r measure7-population, echo=TRUE, message=F, eval=TRUE, cache=TRUE}

set.seed(228)
population_7 <- declare_population(
  households_7 = add_level(N=1000, #Homeowners in CABY High  Priority region 
     AR_contact=sample(c(rep(0,500),rep(1,500))), # of residents in high priority area that connect with AR
     consent=correlate(given = AR_contact, rho = 0.5,
                         draw_binary, prob = 0.5)
))
pop_7 <- population_7() #using Declare Design here to create a population of 500 households, 250 of are located on the main road. Then, we're telling R to use whether or not households are on their main road to determine their level of #there is a direct correlation between who has riparian rights and having willingness to pay to protect the watershed

kable(table(pop_7$AR_contact,pop_7$consent)) %>% 
  add_header_above(c("AR Contact"=1,"Consent to do Prescribed Burn"=2))

```
- For residents in contact with AR, the chance of responding is 50%
- For residents not in contact with AR, the chance of responding is 20%
```{r Measure7, echo=FALSE, message=F, eval=TRUE}
## Declaring response bias


reporting_7 <- declare_assignment(blocks=AR_contact,
                  assignment_variable = "R", 
                  block_prob=c(0.2,0.5)) #PH: using declare_assignment to block random assign (RA) households to the reporting category. Note that households on in contact with AR are more likely to be "reporters" (R==1), meaning that they are more likely to mail a response to the survey.
pop_7 <- reporting_7(pop_7)
```

```{r resp-tab, echo=FALSE}
kable(table(pop_7$AR_contact,pop_7$R)) %>% 
    add_header_above(c("AR Contact"=1,"Respond to Survey"=2))

```

Reporting and Sampling  
```{r measure7-report-samp}

sims_7 <- 1000 #simulations
sam.n_7 <- 500 #attempted sample size

store_7 <- rep(NA, sims_7)
for (i in 1:sims_7){
  store_7[i] <- mean(pop_7[sample(1:500,sam.n_7),] %>%
                     filter(R==1) %>%
                     pull(consent))} 

#PH: in this for-loop, we're taking a random sample of households, subsetting out those that are "non-reporters" (R==0) and then taking the mean of their willingness to consent to prescribed burns. We do this "sims" number of times (1000).

summary(store_7)
```

```{r}
sam.dist_7 <- ggplot(data.frame(store_7), aes(x=store_7)) + 
  geom_histogram(color="black", fill="white") +
  xlab("Mean value of sample") +
  geom_vline(xintercept = mean(pop_7$consent), linetype="dashed", 
                color = "blue", size=1.5)
sam.dist_7 #PH: the blue dashed vertical line represents the "true" population mean of household satisfaction, while the underlying histogram plots the mean level of satisfaction among "reporting" households we calculated for each of the 1000 draws from the sample. This figure demonstrates response bias, in that it shows how systematically excluding units -- in this case, households -- that have a lower probably of responding leads to an overestimate of the population parameter of interest -- in this case, mean levels of satisfaction.
```


